Explore the SingleR results

### 2025-07-25 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/singler-results.Rmd
Update analyses/cell-type-neuroblastoma-04/exploratory-notebooks/singler-results.Rmd
Co-authored-by: Ally Hawkins <54039191+allyhawkins@users.noreply.github.com>

```{r, fig.width = 8, fig.height = 8}
make_jaccard_heatmap(
  celltype_recoded_wide_df |> dplyr::filter(library_id %in% libraries_low_cells$library_id),
  "consensus_validation",
  "singler",
  "Consensus validation label",
  "SingleR NBAtlas label"
)
```

>>>>

```{r, fig.width = 8, fig.height = 8}
low_cells_df <- celltype_recoded_wide_df |> 
  dplyr::filter(library_id %in% libraries_low_cells$library_id)

make_jaccard_heatmap(
  low_cells_df,
  "consensus_validation",
  "singler",
  "Consensus validation label",
  "SingleR NBAtlas label"
)
```
